---
title: "Unit6 Case Study"
author: "Marvin Scott"
date: "June 12, 2016"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### INTRODUCTION
The objective of this document is to illustrate via R programming  the data munging and analytical processes invloved between datasets listed below

#####        * (1)GDP Rank
#####        * (2)Ed Stats

### DOWNLOAD PROCESS
#####        * (1)GDP Rank
######LOAD FILE INTO WORKSPACE AFTER SAVING INTO DIRECTORY 
gross <-read.csv("GDP.csv", stringsAsFactors = FALSE, skip= 5, nrows = 231,  header  =FALSE)

#####        * (2)Ed Stats
######LOAD FILE INTO WORKSPACE AFTER SAVING INTO DIRECTORY 
edstat <-read.csv("Edstats_Country.csv", stringsAsFactors = TRUE,   header  =TRUE)

### TIDYING PROCESS
#####        * (1)GDP Rank
######NAME vARIBLES
names(gross)<- c("COUNTRYCODE", "RANKING", "JUNK1", "ECONOMY","US_DOLLARS_MILLIONS", "JUNK2", "JUNK3", "JUNK4", "JUNK5", "JUNK6")

######OBSERVE DATA TYPES ANS VALUES
str(gross)

######LOAD PACKAGES
library(plyr)
library(dplyr)

######SPECIFIY VARIABLE SELECTION REQ'D FOR ANALYSIS
grossx<-select(gross, COUNTRYCODE,RANKING, ECONOMY , US_DOLLARS_MILLIONS)

######CHANGE DATA TYPE TO "FACTOR"
grossx$COUNTRYCODE<-as.factor(grossx$COUNTRYCODE)

######CHANGE DATA TYPE TO "FACTOR"
grossx$ECONOMY<-as.factor(grossx$ECONOMY)

######CHECK MISSING VALUES/NAs
summary(grossx)

######CHECK NAs 
count(is.na(grossx$RANKING))
count(is.na(grossx$US_DOLLARS_MILLIONS))

#####        * (2)Ed Stats

######OBSERVE DATA TYPES ANS VALUES
str(grossx)

######NAME vARIBLES
names(edstat)[2]<- "SHORTNAME"
names(edstat)[9]<- "INCOMEGROUP"
names(edstat)[1]<- "COUNTRYCODE"

######SPECIFIY VARIABLE SELECTION REQ'D FOR ANALYSIS
edstat_gdp<-select(edstat, COUNTRYCODE,SHORTNAME, INCOMEGROUP)

######CHECK MISSING VALUES/NAs
str(edstat_gdp)
summary(edstat_gdp)

### MERGING PROCESS FOR (1) GDP Rank & (2)Ed Stats DATASETS
######MERGE DATA BY "**COUNTRYCODE**"
mergedata1<-merge(x=edstat_gdp, y= grossx , by = "COUNTRYCODE", all= TRUE)
head(mergedata1)

### CODE PURPOSE

```{r}
gross <-read.csv("GDP.csv", stringsAsFactors = FALSE, skip= 5, nrows = 231,  header  =FALSE)
######LOAD FILE INTO WORKSPACE AFTER SAVING INTO DIRECTORY 
edstat <-read.csv("Edstats_Country.csv", stringsAsFactors = TRUE,   header  =TRUE)
######NAME vARIBLES
names(gross)<- c("COUNTRYCODE", "RANKING", "JUNK1", "ECONOMY","US_DOLLARS_MILLIONS", "JUNK2", "JUNK3", "JUNK4", "JUNK5", "JUNK6")
######OBSERVE DATA TYPES ANS VALUES
str(gross)
######LOAD PACKAGES
library(plyr)
library(dplyr)
######SPECIFIY VARIABLE SELECTION REQ'D FOR ANALYSIS
grossx<-select(gross, COUNTRYCODE,RANKING, ECONOMY , US_DOLLARS_MILLIONS)
######CHANGE DATA TYPE TO "FACTOR"
grossx$COUNTRYCODE<-as.factor(grossx$COUNTRYCODE)
######CHANGE DATA TYPE TO "FACTOR"
grossx$ECONOMY<-as.factor(grossx$ECONOMY)
######CHECK MISSING VALUES/NAs
summary(grossx)


######CHECK NAs 
######count(is.na(grossx$RANKING))
######count(is.na(grossx$US_DOLLARS_MILLIONS))

######OBSERVE DATA TYPES ANS VALUES
str(grossx)
######NAME vARIBLES
names(edstat)[2]<- "SHORTNAME"
names(edstat)[9]<- "INCOMEGROUP"
names(edstat)[1]<- "COUNTRYCODE"
######SPECIFIY VARIABLE SELECTION REQ'D FOR ANALYSIS
edstat_gdp<-select(edstat, COUNTRYCODE,SHORTNAME, INCOMEGROUP)
######CHECK MISSING VALUES/NAs
str(edstat_gdp)
summary(edstat_gdp)

### MERGING PROCESS FOR (1) GDP Rank & (2)Ed Stats DATASETS
######MERGE DATA BY "**COUNTRYCODE**"
mergedata1<-merge(x=edstat_gdp, y= grossx , by = "COUNTRYCODE", all= TRUE)
head(mergedata1)



```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
